---
title: "Running"
output: 
  html_document:
    css: main.css
---
<nav>
  <ul>
	  <li><a href="/">About</a></li>
    <li><a href="/cv">CV</a></li>
		<li><a href="/running">Running</a></li>
    <li><a href="/blog">Blog</a></li>
	</ul>
</nav>


***

#### 2019 Kansas City Marathon

```{r fig.width=10, fig.height=7, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2019-10-19.png')
grid.raster(img)
```

***

#### 2019 Hospital Hill Half Marathon

```{r fig.width=10, fig.height=7, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2019-06-01.png')
grid.raster(img)
```

***

#### 2018 Kansas City Half Marathon

```{r fig.width=10, fig.height=7, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2018-10-20.png')
grid.raster(img)
```

***

#### 2018 Hospital Hill Half Marathon

```{r fig.width=10, fig.height=7, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2018-06-02.png')
grid.raster(img)
```

***

#### 2017 Kansas City Half Marathon

```{r fig.width=10, fig.height=7, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2017-10-21.png')
grid.raster(img)
```

***

#### 2017 Hospital Hill Half Marathon

```{r fig.width=7, fig.height=10, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2017-06-03.png')
grid.raster(img)
```

***

#### 2016 Des Moines Turkey Trot 5K

```{r fig.width=10, fig.height=10, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2016-11-26.png')
grid.raster(img)
```

***

#### 2016 Kansas City Marathon

```{r fig.width=7, fig.height=10, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2016-10-15.png')
grid.raster(img)
```

***

#### 2014 Kansas Half Marathon

```{r fig.width=10, fig.height=10, echo=FALSE, message=FALSE,warning=FALSE}
library(png)
library(grid)

img <- readPNG('2014-11-03.png')
grid.raster(img)
```

***

#### 2013 Kansas City Half Marathon

```{r fig.width=7, fig.height=10, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2013-10-19.png')
grid.raster(img)
```

***

#### 2012 Kansas City Half Marathon

```{r fig.width=7, fig.height=10, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2012-10-20.png')
grid.raster(img)
```

***

#### 2012 Hy-Vee 5150 Triathalon

```{r fig.width=7, fig.height=10, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2012-09-02.png')
grid.raster(img)
```

***

#### 2011 Kansas City Marathon

```{r fig.width=7, fig.height=10, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2011-10-15.png')
grid.raster(img)
```

***

#### 2010 Kansas City Marathon

```{r fig.width=7, fig.height=10, echo=FALSE}
library(png)
library(grid)

img <- readPNG('2010-10-16.png')
grid.raster(img)
```

***

<nav>
  <ul>
	  <li><a href="/">About</a></li>
    <li><a href="/cv">CV</a></li>
		<li><a href="/running">Running</a></li>
    <li><a href="/blog">Blog</a></li>
	</ul>
</nav>

<center> Copyright © 2020 Jeremy B Provance </center>












